Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-04-25 ms.tex
Added postage stamps and a reference-corrected time series for UT Aug 12.

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps_r09px_cen.pdf}
\caption{Postage stamps of apertures used for each source, after centroiding and using a wider 9 pixel source aperture.}\label{fig:starPostageCenAp9px}
\end{centering}
\end{figure}

When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{}.
The Kepler-based ephemeris indicates a transit at JD = 2457551.830.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830.}\label{fig:refCorrectedPhotAug12}
\end{centering}
\end{figure}
